\bf Effects of Word Alignment Visualization on Post-Editing Quality \& Speed

### 2015-07-10 paper/paper_methodology.tex
Merge in Isabel's methodology changes

We hypothesize that the presentation of word-level alignment links to human post-editors may affect the quality or speed of the resulting output, and that such effects may be dependent on the quality of the underlaying machine translations.
%
To test this hypothesis, we conduct a bilingual post-editing experiment  where bilingual post-editors are presented with machine translation output of varying quality, with and without word-level alignment link visualization.

@@

There were four participants who served as post-editors in the Spanish-English portion of this study, all of whom were paid for their time. 
%
They were all Spanish-English bilinguals.
%
We designate these participants as PE7--PE10.
%
The first language (L1) of all four participants was English, and all four were highly proficient in Spanish as their second language (L2). 
%
These participants were second year students in a university Master of Spanish Translation program.

@@

Two Spanish source texts were selected. Both were extracts from a news article from a Spanish newspaper covering current world news events. 
%
The two texts were divided up into segments that corresponded to sentences or stand alone phrases. 
%
The first text had 26 segments that varied in length from 4 to 24 words (mean length 15 words) and the second text had 25 segments that varied in length from 4 to 28 words (mean length 16 words).
%
We designate the former as Doc C and the latter as Doc D.
%
No reference translations exist for either Spanish text.

@@

Participants post-edited one text using the interface where alignment links were shown and the other text using the interface where alignment links were omitted. 
%
Participants post-edited the two texts in one session lasting less than one hour. 
%
Post-editors 7 and 9 edited Doc C using the interface that omitted the alignments and Doc D using the interface that displayed the alignments. 
%
Post-editors 8 and 10 edited Doc C using the interface that displayed the alignments and Doc D using the interface that omitted the alignments.

>>>>

We hypothesize that the presentation of word-level alignment links to human post-editors may affect the quality or speed of the resulting output, and that such effects may be dependent on the quality of the underlying machine translations.
%
To test this hypothesis, we conduct a bilingual post-editing experiment where bilingual post-editors are presented with machine translation output of varying quality, with and without word-level alignment link visualization.

@@

There were eleven participants who served as post-editors in the Spanish-English portion of this study, all of whom were paid for their time. 
%
They were all Spanish-English bilinguals.
%
We designate these participants as PE7--PE17. 
%
The first language (L1) of all eleven participants was English, and all eleven were highly proficient in Spanish as their second language (L2). 
%
These participants were students in a university Master of Spanish Translation program.

@@

Two Spanish source texts were selected. Both were extracts from a news article from a Spanish newspaper covering current world news events. 
%
The two texts were divided up into segments that corresponded to sentences or stand-alone phrases. 
%
The first text had 26 segments that varied in length from 4 to 24 words (mean length 15 words) and the second text had 25 segments that varied in length from 4 to 28 words (mean length 16 words).
%
We designate the former as Doc C and the latter as Doc D.
%
No reference translations exist for either Spanish text.

@@

Participants post-edited one text using the interface where alignment links were shown and the other text using the interface where alignment links were omitted. 
%
Participants post-edited the two texts in one session lasting less than one hour. 
%
Post-editors 7, 9, 11, 13, 15, and 17 edited Doc C using the interface that omitted the alignments and Doc D using the interface that displayed the alignments. 
%
Post-editors 8, 10, 12, 14, and 16 edited Doc C using the interface that displayed the alignments and Doc D using the interface that omitted the alignments.
